Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-22 doc/asplos13/grappa.tex
fixed small issues

\begin{figure}[htbp]
  \begin{center}
    \begin{description}\small
      \item[ \texttt{ global\_address global\_malloc( size )} ] \hfill \\
      \item[ \texttt{ global\_free( global\_address )} ] \hfill \\
        Allocates and frees memory in the global heap
      \item[ \texttt{ delegate\_read( global\_address, local\_var )} ] 
      \item[ \texttt{ delegate\_write( global\_address, local\_var )} ] \vspace{-2ex}
      \item[ \texttt{ delegate\_cas( global\_address, local\_var )} ] \vspace{-2ex}
      \item[ \texttt{ delegate\_inc( global\_address, local\_var )} ] \vspace{-2ex} \hfill \\
        Performs a memory operation at the home core of a global address
      \item[ \texttt{ cache\_acquire( global\_address, local\_buf, \{RO,RW,WO\})} ]
      \item[ \texttt{ cache\_release( global\_address, local\_buf )} ] \vspace{-2ex} \hfill \\
        Perform cache operations \TODO{expand}
    \end{description}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:accessing-memory} Grappa API: accessing memory} %{-4ex}}
    \end{minipage}
    %\vspace{-3ex}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \begin{description}\small
      \item[ \texttt{ global\_address global\_malloc( size )} ] \hfill \\
      \item[ \texttt{ global\_free( global\_address )} ] \hfill \\
        Allocates and frees memory in the global heap
      \item[ \texttt{ delegate\_read( global\_address, local\_var )} ] 
      \item[ \texttt{ delegate\_write( global\_address, local\_var )} ] %\vspace{-2ex}
      \item[ \texttt{ delegate\_cas( global\_address, local\_var )} ] %\vspace{-2ex}
      \item[ \texttt{ delegate\_inc( global\_address, local\_var )} ] %\vspace{-2ex} 
\hfill \\
        Performs a memory operation at the home core of a global address
      \item[ \texttt{ cache\_acquire( global\_address, local\_buf, \{RO,RW,WO\})} ]
      \item[ \texttt{ cache\_release( global\_address, local\_buf )} ] %\vspace{-2ex} 
\hfill \\
        Perform cache operations \TODO{expand}
    \end{description}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:accessing-memory} Grappa API: accessing memory} %{-4ex}}
    \end{minipage}
    %\vspace{-3ex}
  \end{center}
\end{figure}
